---
output: github_document
---

# *cnvs*: A (highly) opinionated interface with the Canvas VLE

Or, if you like: Taking the "AAAAA" out of Canvas (get it?)

Note that **this package is designed to work specifically with Canvas at the University of Sussex**, particularly in the School of Psychology, and I make no guarantees whatsoever that it will work for anyone else. I've tried to build in the possibility for variation, but do let me know if you want to use the package and are finding its (i.e. my) opinions are causing problems!

## Installation

```{r, eval=FALSE}

if(!require(remotes)){
  install.packages('remotes')
}

remotes::install_github("drmankin/cnvs")
```

## Setup

In order to work with Canvas, you will need two key elements:

-   A Canvas token
-   Your institution's Canvas URL

This information will be stored locally in your .Renviron file to authenticate your requests. This only needs to be done **once** per terminal, or if your information changes (e.g. you move institutions).

### Canvas Token

To obtain a Canvas access token:

-   Log into Canvas.
-   Click on your profile picture, then on Settings.
-   Click on the "+ New access token" button and follow the instructions.

**Pro-tip**: Save your Canvas token somewhere safe, where you can find it again. For example, paste it into a simple text document and save it as `canvas_token.txt` in a sensible place in your folders. Once you leave the page where it's displayed, you cannot retrieve it again!

### Canvas Domain

To obtain the Canvas domain:

-   Navigate in your browser to your Canvas dashboard
-   The Canvas domain is everything after `https://`, typically `canvas.your_uni_domain`, e.g. `canvas.sussex.ac.uk`

### Storing .Renviron values

<!-- This package includes an interactive function to edit the .Renviron file with the correct variable names. After package installation, when you have both your Canvas token and domain to hand, run the following in the Console: -->

<!-- ```{r, eval=FALSE} -->

<!-- cnvs::set_renv_variables() -->

<!-- ``` -->

To create the variables manually, open your .Renviron file, for example using the `usethis` package:

```{r, eval=FALSE}
if(!require(remotes)){
  install.packages('usethis')
}

usethis::edit_r_environ()
```

Then, paste the following into the .Renviron file, replacing the placeholders with your own information and ensuring that there is a blank line at the end of the file:

```{r, eval=FALSE}

CANVAS_TOKEN = "your_canvas_token"
CANVAS_DOMAIN = "your_canvas_domain"

```

Save the .Renviron file and close it.

Make sure that you **restart your R session** for the .Renviron changes to take effect.

## Getting Started

Begin any work with `cnvs` with the following:

```{r, eval=FALSE}

library(cnvs)
cnvs::canvas_setup()
```

The function `cnvs::canvas_setup()` will set your token and domain and establish a connection with the Canvas API, which is essential for any further requests. This function needs to run at the start of every new session - so will need to be rerun if e.g. your session crashes.

You're now ready to go!

<!-- ## Tasks -->

<!-- The following vignettes will demonstrate a recommended workflow for some tasks you might be interested in -->

<!-- - Getting student and module information -->

<!-- - Creating quizzes -->

<!-- - Creating pages with Quarto -->

<!-- - Pulling grades -->

<!-- - Getting assessment information -->

## Notes on Working with `cnvs`

This package tries to streamline the iterative nature of querying the Canvas API. For essentially any information that Canvas holds - for users, assessments, questions in a quiz, answers to a particular question, there is a corresponding ID number that Canvas uses to identify that specific thing. These functions generally try to truncate the back-and-forth by making assumptions about the end goal.

The way this package is built is to absolutely minimise the amount of time you ever have to leave R to interact with Canvas directly. Some of these are data-management operations to get student, assessment etc. data; and some are just because I personally hate having to click on things (see e.g. `cnvs::quarto_annc` and `cnvs::quarto_page` for writing and posting announcements and pages in Canvas using Quarto, for instance).

This package also has a LOT of opinions about what information you need or want; how it should be formatted; and what you're going to do with it. Generally speaking, they're convenience functions for more generally applicable [`rcanvas`](https://github.com/daranzolin/rcanvas) functions to make my life easier for my common tasks. You may find that the relevant `rcanvas` function makes fewer assumptions about what you want to do, and may be better suited to your needs so you can customise/format/wrangle the output as you like. I hope you find these functions useful, though! Let me know if there's anything that doesn't work or needs tweaking to make it more helpful.

### Terminology

Canvas itself is an American company; I work at a university in the UK. This means that there are certain, unfortunate, weird vocabulary mismatches that could be *very* confusing (separated by a common language, innit).

| American/Canvas Default | UK/Sussex | Notes |
|------------------------|------------------------|------------------------|
| Assignment | Assessment | Sometimes also "Assignment"! Generally I've stuck with "assignment" in the code but sometimes "assessment" in formatting/output. |
| Course | Module | This is the big one. "Course" in the UK refers to the whole degree programme, and individual classes are called "modules". The most important ID number you'll typically need to work with `cnvs` will be `module_id`; see `cnvs::get_module_id()` for more info. Confusingly, the API query still uses "courses" - but I'm set in my ways now. |
| Grade | Mark | Minor - I use both, but UK usage tends towards "mark". |
| Module | Unit | See, this is where it gets messy. Canvas DOES make use of the term "module", but the default usage is for [grouped blocks of content](https://www.instructure.com/resources/blog/how-use-modules-build-courses-canvas). Since the UK term for a "course" is a "module", we instead refer to this sense of "module" as a "unit". So, in the US (and by Canvas default) you'd have *modules* of content within your *course*, which all together form your *degree*; in the UK (or,at least, at Sussex) you'd have *units* of content in your *module*, which altogether form your *course*. Clear as mud! |
| Section | Section | Thankfully for my sanity and yours, organisations of students within a [course/module] are called "sections" no matter what. Sense prevails for the first and only time. |
