---
title: "week_page_template"
format: html
self-contained: true
---

```{r}
#| eval: false

cnvs::canvas_setup()

web_url <- "https://analysingdata.pages.dev/content"

posit_url <- "htts://posit.cloud"

week_number <- "01"

cnvs::embed_link(link_text = "Lecture slides", web_url = file.path(web_url, "lectures", paste0("lecture_", week_number)), dest = "website", type = "html")
```

## Lecture

This week's lecture will be on `lecture_title`.

`r cnvs::embed_link(link_text = "Lecture slides", web_url = file.path(web_url, "lectures", paste0("lecture_", week_number)), dest = "website")`

`r cnvs::embed_link(link_text = "Lecture recording", dest = "Panopto Recordings")`

## Practical

This week's practical will cover 

## Tutorial

```{r}
type <- "tutorials"
tut_name <- paste0("Tutorial", week_number)
```

The tutorial for this week is `r tut_name`. Work through the tutorial on Posit Cloud, or read the tutorial separately here.

## Quiz

`r quiz`.

`r cnvs::embed_link("Go to Quizzes", "Quizzes")`
